Prediction maps of defoliation at trees

### 2019-05-23 analysis/report-defoliation.Rmd
wflow_publish(all = T)

```{r echo = FALSE}
system("rsync -rlptDvzog --chown=www-data:www-data --fake-super /home/patrick/papers/2019-feature-selection/analysis/report-defoliation.html -e ssh patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/"
       )
```

>>>>

```{r echo = FALSE}
system("rsync -rlptDvzog --chown=www-data:www-data --fake-super /home/patrick/papers/2019-feature-selection/docs/report-defoliation.html -e ssh patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/"
       )
```
